---
title: "Final Project"
author: "Hope Kudo"
date: "11/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
library(tidyverse)
library(ggplot2)
library(atus)
library(shinythemes)
library(skimr)
library(readxl)
library(janitor)
```

```{r}

cps <- atuscps
time <- atusact
resp <- atusresp

table <- left_join(cps, resp, by = "tucaseid")
View(table)

#View(cps)
            
            



```

Notes:
cps: This is a 181,335 by 13 data frame containing information collected in the CPS about all individuals who were selected for and responded to the ATUS. The 'tucaseid' variable identifies unique households. 
time/act: A data frame with 2,094,140 observations on the following variables: tucaseid, time use survey
resp: This is a 181,335 by 22 data frame containing information on the respondents, including their employment, household, and the diary day (day on which they were interviewed).

has data from 2003 - 2016


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
